---
title: "shinyr: Data Insights Through an Inbuilt R Shiny App"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shinyr: Data Insights Through an Inbuilt R Shiny App}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The package 'shinyr' provides data insights through an inbuilt R shiny app.

```{r setup}
library(shinyr)
```

1. Do you want to get insights into your data without much effort?
2. Do you want to build a shiny dashboard for your own data?
3. Do you want to analyse your data by subsetting it dynamically? 
4. Do you want to perform an initial analysis of your data with just a few clicks?

All these are possible with the package- 'shinyr' without doing much programming! You have to run one single command and upload your data. 

```{r, eval=FALSE, message=FALSE, warning=FALSE}
shinyr::shineMe()
```

#### Remember, your data stays safe! Your data will not be exposed to anyone/anywhere.